---
format:
  typst:
    include-before-body: 
      - file: 'header.typ'
    mainfont: 'Oswald'
    fig-format: svg
    fig-dpi: 600
params:
  md_input:
  data_path: 
  image1:
  image2:
  image3:
knitr:
  opts_chunk:
    dev: svg
---

```{r setup, include=FALSE}

# Configured default plotting dimensions for landscape letter size
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(ggimage)
library(tinytable)

```

```{r, eval=F}
load("stats_period.RData")
md_input <- "13th June 2026 - MD 7 vs Calgary (H)"
md_date <- stats_period %>% filter(activity_name==md_input) %>% mutate(date = paste0(weekdays(date), ', ', format(date, '%B %d, %Y'))) %>% pull(date) %>% unique
md_num <- str_extract(md_input, '(?<=MD\\s)\\d{1}')
md_year <- str_extract(md_date, '\\d{4}')
image1 <- "TidesFCImage5.jpg"
image2 <- "TidesFCImage6.jpg"
image3 <- "TidesFCImage7.jpg"

team_logo <- case_when(str_detect(md_input, "Montreal") ~ "Montreal.png",
                       str_detect(md_input, "Ottawa") ~ "Ottawa.png",
                       str_detect(md_input, "Toronto") ~ "Toronto.png",
                       str_detect(md_input, "Calgary") ~ "Calgary.png",
                       str_detect(md_input, "Vancouver") ~ "Vancouver.png",
                       str_detect(md_input, "Portsmouth") ~ "Portsmouth.png",
                       str_detect(md_input, "Everton") ~ "Everton.png",
                       str_detect(md_input, "West Ham") ~ "West Ham.png",
                       str_detect(md_input, "AUS") ~ "AUS.png")
```

```{r}
data_path <- params$data_path

stats_period <- readRDS(data_path)

md_input <- params$md_input

image1 <- params$image1

image2 <- params$image2

image3 <- params$image3

if (is.null(image1)) {
  image1 <- 'TidesFCImage5.jpg'
}
if (is.null(image2)) {
  image2 <- 'TidesFCImage6.jpg'
}
if (is.null(image3)) {
  image3 <- 'TidesFCImage7.jgp'
}

md_date <- stats_period %>% filter(activity_name==md_input) %>% mutate(date = paste0(weekdays(date), ', ', format(date, '%B %d, %Y'))) %>% pull(date) %>% unique
md_num <- str_extract(md_input, '(?<=MD\\s)\\d{1,2}')
md_year <- str_extract(md_date, '\\d{4}')

team_logo <- case_when(str_detect(md_input, "Montreal") ~ "Montreal.png",
                       str_detect(md_input, "Ottawa") ~ "Ottawa.png",
                       str_detect(md_input, "Toronto") ~ "Toronto.png",
                       str_detect(md_input, "Calgary") ~ "Calgary.png",
                       str_detect(md_input, "Vancouver") ~ "Vancouver.png",
                       str_detect(md_input, "Portsmouth") ~ "Portsmouth.png",
                       str_detect(md_input, "Everton") ~ "Everton.png",
                       str_detect(md_input, "West Ham") ~ "West Ham.png",
                       str_detect(md_input, "AUS") ~ "AUS.png")
```

---
# Dynamically pass the R variable to Quarto metadata
image1: '`r image1`'
image2: '`r image2`'
image3: '`r image3`'
team_logo: '`r team_logo`'
md_date: '`r md_date`'
md_input: '`r md_input`'
md_num: '`r md_num`'
md_year: '`r md_year`'
---


```{=typst}

#show heading: set align(center)


#set table(inset: (x, y) => (
  x: 5pt,
  y: if y == 0 { 5pt } else { 2.5pt }
))


// Page 1 Visual Layout Context Frame
#align(center + horizon)[
  #grid(
    columns: 3,
    gutter: 1cm,
    image("Halifax.png", width: 5cm),
    image("vs.png", width: 5cm),
    image("{{< meta team_logo >}}", width: 5cm)
  )
  #v(1cm)
  #text(size: 60pt, weight: "bold")[MATCH REPORT] \
  #v(0.4cm)
  #text(size: 30pt, style: "italic", fill: rgb("#00B0B9"))[Season {{< meta md_year >}} - Game {{< meta md_num >}}] \
  #v(1cm)
  #text(size: 24pt)[{{< meta md_date >}}]
]
```


{{< pagebreak >}}

```{=typst}

// Page 2 Section Divider
#section-page("{{< meta image1 >}}", "SQUAD GAME DATA")
```

{{< pagebreak >}}


```{r}

match_day_summary <- stats_period %>% 
  dplyr::filter(activity_name == md_input & str_detect(period_name, "^\\d{1,2}\\. [[:alpha:]]{5,6} Half$")) %>%
  select(activity_name, position_name, athlete_name, period_name, field_time, total_distance, high_speed_distance, sprint_distance, accel_efforts, decel_efforts,max_vel_kph) %>% 
  mutate(across(where(is.numeric), ~if_else(field_time == 0 & total_distance == 0, NA_real_, .x))) %>% 
  pivot_wider(names_from = period_name, names_glue = "{period_name}_{.value}", values_from = c(field_time, total_distance, high_speed_distance, sprint_distance, accel_efforts, decel_efforts,max_vel_kph)) %>% 
  mutate(Sub = if_else(is.na(`2. First Half_field_time`) | `2. First Half_field_time` < (10*60), T, F)) %>% 
  pivot_longer(cols=contains(". "), names_to = c("period_name", ".value"), names_pattern = "(\\d{1,2}\\. [[:alpha:]]{5,6} Half)_(.*)") %>% 
  group_by(activity_name, athlete_name, position_name, Sub) %>% 
  summarize(across(where(is.numeric) & !max_vel_kph, ~sum(.x,na.rm=T)), max_vel_kph = max(max_vel_kph, na.rm=T)) %>% 
  ungroup %>% 
  mutate(`%HSR+Sprint Distance` = ((high_speed_distance+sprint_distance)/total_distance),
         field_time=field_time/60) %>% 
  relocate(`%HSR+Sprint Distance`, .before=max_vel_kph) %>% 
  relocate(Sub, .after=max_vel_kph) %>% 
  relocate(field_time, .before=total_distance) %>% 
  rename(Match = activity_name, Player = athlete_name, Position = position_name,`Total Distance (m)` = total_distance, `HSR Distance (m)` = high_speed_distance, `Sprint Distance (m)` = sprint_distance, 
         `Accel Efforts` = accel_efforts, `Decel Efforts`=decel_efforts, `Max Speed (kph)` = max_vel_kph, `Time (min)` = field_time) %>% 
  mutate(Position = case_when(str_detect(Position, "Keeper")~ "Keeper",
                              str_detect(Position, "Back") | str_detect(Position, "Defender")~ "Defender",
                              str_detect(Position, "Midfielder")~ "Midfielder",
                              str_detect(Position, "Winger") | str_detect(Position, "Striker")~ "Attacker",
                              .default=Position),
    Position=factor(Position, levels=c("Keeper", "Defender", "Midfielder", "Attacker"))) %>% 
  arrange(Sub, Position) %>%  
  mutate(
    `%HSR+Sprint Distance` = scales::percent(`%HSR+Sprint Distance`, accuracy =0.01),
    across(where(is.numeric) & ! `Max Speed (kph)`, round), 
    `Max Speed (kph)`=round(`Max Speed (kph)`,1)
  ) %>%
  select(-c(Position,Match)) 


names(match_day_summary)[names(match_day_summary) == "Time (min)"] <- format_tt("Time (min)", escape = "typst")
names(match_day_summary)[names(match_day_summary) == "Total Distance (m)"] <- format_tt("Total Distance (m)", escape = "typst")
names(match_day_summary)[names(match_day_summary) == "HSR Distance (m)"] <- format_tt("HSR Distance (m)", escape = "typst")
names(match_day_summary)[names(match_day_summary) == "Sprint Distance (m)"] <- format_tt("Sprint Distance (m)", escape = "typst")
names(match_day_summary)[names(match_day_summary) == "Max Speed (kph)"] <- format_tt("Max Speed (kph)", escape = "typst")


# Custom function with dynamic color arguments
ggplot_progress_bar <- function(x, data_column, bar_fill = "#00B0B9", bar_outline = "#FFFFFF", text_color = "#FFFFFF", ...) {
  min_limit <- min(data_column, na.rm=T)
  max_limit <- max(data_column, na.rm=T)
  scaled <- (x-min_limit)/(max_limit-min_limit)
  # scaled <- x/max_limit
  df <- data.frame(val = x, scaled = scaled, max_val = 1)
  
  p <- ggplot(df) +
    #Background bar
    geom_col(aes(x = max_val, y = 1), fill = "transparent", linewidth =1, color = bar_outline, width = 0.2) +
    #Foreground bar 
    geom_col(aes(x = scaled, y = 1), fill = bar_fill, linewidth =1,color = bar_outline, width = 0.2) +
    geom_text(aes(x = max_val/2, y = 1, label = val), color=text_color, hjust = "middle",fontface="bold", size = 16) +
    scale_x_continuous(expand = c(0.05, 0.05)) +
    scale_y_discrete(expand = c(0.01,0.01)) +
    theme_void()

}



match_day_summary %>%
  tt() %>% 
  theme_empty() %>% # Clear out the default black theme lines
  style_tt(i = 0, line = "tb", line_color = "#FFFFFF", line_width = 0.05) %>%
  style_tt(i = nrow(match_day_summary), line = "b", line_color = "#FFFFFF", line_width = 0.05) %>% 
  format_tt(escape=T) %>% 
  # theme_tt("spacing", "compact")  %>%
  # style_tt(background = "#FFFFFF", color = "#221C35") %>% 
  style_tt(align = "lcccccccc", alignv = "m",line_color = "#FFFFFF") %>% 
  style_tt(i = "colnames", bold = TRUE, alignv = "t") %>%
  style_tt(i=Sub == TRUE, j=Player, color = "#00B0B9") %>% 
  subset(select = -Sub) %>% 
  plot_tt(j = 3, fun = ggplot_progress_bar,height=2, data = as.list(match_day_summary$`Total Distance (m)`), data_column=match_day_summary$`Total Distance (m)`, bar_fill = "#00B0B9", bar_outline  = "#FFFFFF", text_color= "#FFFFFF")  %>% 
  plot_tt(j = 4, fun = ggplot_progress_bar,height=2, data = as.list(match_day_summary$`HSR Distance (m)`), data_column=match_day_summary$`HSR Distance (m)`, bar_fill = "#572C5F", bar_outline  = "#FFFFFF", text_color= "#FFFFFF") %>% 
  plot_tt(j = 5, fun = ggplot_progress_bar,height=2, data = as.list(match_day_summary$`Sprint Distance (m)`), data_column=match_day_summary$`Sprint Distance (m)`, bar_fill = "#00B0B9", bar_outline  = "#FFFFFF", text_color= "#FFFFFF") %>% 
  plot_tt(j =6, fun = ggplot_progress_bar,height=2, data = as.list(match_day_summary$`Accel Efforts`), data_column=match_day_summary$`Accel Efforts`, bar_fill = "#572C5F", bar_outline  = "#FFFFFF", text_color= "#FFFFFF") %>% 
  plot_tt(j = 7, fun = ggplot_progress_bar,height=2, data = as.list(match_day_summary$`Decel Efforts`), data_column=match_day_summary$`Decel Efforts`, bar_fill = "#00B0B9", bar_outline  = "#FFFFFF", text_color= "#FFFFFF") 
# %>% 
  # plot_tt(j = 3, fun = "bar",height=0.7, data=as.list(match_day_summary$`Total Distance (m)`), color = c("#00B0B9","#E5E1E6"), sprintf = paste0("%s", match_day_summary$`Total Distance (m)`))%>% 
  # style_tt(j = 3, i = "~groupi",fontsize = 0.7) %>% 
  # plot_tt(j = 4, fun = "bar",data=as.list(match_day_summary$`HSR Distance (m)`), color = c("#572C5F","#E5E1E6"), sprintf = paste0("%s", match_day_summary$`HSR Distance (m)`))%>% 
  # plot_tt(j = 5, fun = "bar",data=as.list(match_day_summary$`Sprint Distance (m)`), color = c("#00B0B9","#E5E1E6"), sprintf = paste0("%s", match_day_summary$`Sprint Distance (m)`))%>% 
  # plot_tt(j = 6, fun = "bar",data=as.list(match_day_summary$`Accel Efforts`), color = c("#572C5F","#E5E1E6"), sprintf = paste0("%s", match_day_summary$`Accel Efforts`))%>% 
  # plot_tt(j = 7, fun = "bar",data=as.list(match_day_summary$`Decel Efforts`), color = c("#00B0B9","#E5E1E6"), sprintf = paste0("%s", match_day_summary$`Decel Efforts`))
  

```

{{< pagebreak >}}

#### OVERALL HALF COMPARISON

```{r distance_per_half, fig.width = 9.5, fig.height = 6,dpi=600, dev.args = list(bg = "transparent")}

md_distance_per_half <- stats_period %>% 
  filter(position_name != "Goal Keeper" & activity_name == md_input & str_detect(period_name, "^\\d{1,2}\\. [[:alpha:]]{5,6} Half$")) %>%
  select(activity_name, date, athlete_name, period_name, field_time, total_distance, high_speed_distance, sprint_distance) %>% 
  mutate(across(where(is.numeric), ~if_else(field_time == 0 & total_distance == 0, NA_real_, .x)),
         period_name=str_remove(period_name, "\\d{1,2}\\.\\s")) %>% 
  group_by(activity_name, date, athlete_name, period_name) %>% 
  summarize(across(where(is.numeric), ~sum(.x,na.rm=T))) %>% 
  ungroup %>% 
  group_by(activity_name, date, period_name) %>% 
  summarize(across(where(is.numeric), ~sum(.x,na.rm=T))) %>% 
  ungroup %>%
  mutate(across(c(high_speed_distance, sprint_distance), ~.x*20)) %>% 
  pivot_longer(cols=contains("distance"), names_to = "Type", values_to = "Distance") %>% 
  mutate(Type=factor(Type, levels=c("total_distance", "high_speed_distance", "sprint_distance")), 
         Distance_labels = if_else(Type != "total_distance", round(Distance/20), round(Distance)))

md_distance_per_half %>%
  ggplot(aes(x=period_name, y=Distance))+
  geom_col(aes(fill=Type), position=position_dodge2(width=0.9,preserve = "single")) +
    geom_text(aes(group =Type, label =Distance_labels),size=3.5, vjust = 2, color="white", position=position_dodge2(width=0.9,preserve = "single")) +
  labs(x=NULL, y ="Total Distance (m)",fill=NULL)+
  theme_bw()+
  scale_y_continuous(expand = expansion(mult = c(0, 0.05)), sec.axis = sec_axis(~./20, name="HSR / Sprint Distance (m)"))+
  scale_fill_manual(values=c("#00B0B9","#572C5F","#B2C9D4"),labels = c("Total Distance", "HSR Distance", "Sprint Distance"))+ 
  theme(legend.position = "bottom",legend.direction = "horizontal",panel.grid.major.x=element_blank(), panel.grid.minor.x=element_blank(),
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent", colour = NA),
    legend.box.background = element_rect(fill = "transparent", colour = NA),
    
    # Make all text white
    text = element_text(colour = "white"),
    axis.text = element_text(colour = "white"),
    
    # Make gridlines white
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    
    # Make borders and axis lines white
    panel.border = element_rect(colour = "white", fill = "transparent"),
    axis.line = element_line(colour = "white"),
    axis.ticks.x = element_line(colour = "white"),
    axis.ticks.y = element_line(colour = "white")
 )
```

{{< pagebreak >}}


```{r}
md_distance_by_player <- stats_period %>%
  dplyr::filter(position_name != "Goal Keeper" & activity_name == md_input & str_detect(period_name, "^\\d{1,2}\\. [[:alpha:]]{5,6} Half$")) %>%
  select(activity_name, date, athlete_name, period_name, field_time, total_distance, high_speed_distance, sprint_distance) %>%
  mutate(across(where(is.numeric), ~if_else(field_time == 0 & total_distance == 0, NA_real_, .x)),
         period_name=str_remove(period_name, "\\d{1,2}\\.\\s")) %>%
  group_by(activity_name, date, athlete_name, period_name) %>%
  summarize(across(where(is.numeric), ~sum(.x,na.rm=T))) %>%
  ungroup %>% 
  mutate(across(where(is.numeric) & !field_time, ~.x/(field_time/60), .names="{.col}_per_min"))


```


#### Total Distance and Total Distance/Min By Player (per half)

```{r md_by_player_total_distance,  fig.width=9.5,fig.height=2.8, dpi = 600, dev.args = list(bg = "transparent")}

md_distance_by_player %>% 
  ggplot(aes(x = str_extract(athlete_name,"(?<=\\s)[[:graph:]]+$"), y = total_distance, fill = period_name, label=round(total_distance)))+
  geom_col(position = position_stack(reverse = TRUE))+
  geom_text(position = position_stack(vjust = 0.5,reverse = TRUE),color="white", size=3,check_overlap=T)+
   labs(x=NULL, y ="Total Distance (m)",fill=NULL)+
   theme_bw()+ 
  scale_y_continuous(expand = expansion(mult = c(0, 0.05)))+
    scale_fill_manual(values=c("#572C5F","#00B0B9"))+
  theme(legend.position = "bottom",legend.direction = "horizontal",panel.grid.major.x=element_blank(), panel.grid.minor.x=element_blank(),
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent", colour = NA),
    legend.box.background = element_rect(fill = "transparent", colour = NA),
    
    # Make all text white
    text = element_text(colour = "white"),
    axis.text.y = element_text(colour = "white", size=12),
    axis.text.x = element_text(colour = "white", size=9, angle = 30, hjust = 1, vjust = 1),

    # Make gridlines white
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    
    # Make borders and axis lines white
    panel.border = element_rect(colour = "white", fill = "transparent"),
    axis.line = element_line(colour = "white"),
    axis.ticks.x = element_line(colour = "white"),
    axis.ticks.y = element_line(colour = "white"),
    
    legend.key.size = unit(8, "pt") 
 )
    
  
    
```



```{r md_by_player_total_distance_per_min, fig.width=9.5,fig.height=2.8, dpi = 600, dev.args = list(bg = "transparent")}

md_distance_by_player %>% 
  ggplot(aes(x = str_extract(athlete_name,"(?<=\\s)[[:graph:]]+$"), y = total_distance_per_min))+
  geom_col(aes(fill = period_name),position=position_dodge2(width=0.9,preserve = "single")) +
    geom_text(aes(group =period_name,label=round(total_distance_per_min)),size=3, vjust = -0.5, color="white", position=position_dodge2(width=0.9,preserve = "single")) +
   labs(x=NULL, y ="Total Distance per Min (m/min)",fill=NULL)+
   theme_bw()+ 
  scale_y_continuous(expand = expansion(mult = c(0, 0.12)))+
    scale_fill_manual(values=c("#572C5F","#00B0B9"))+
  theme(legend.position = "bottom",legend.direction = "horizontal",panel.grid.major.x=element_blank(), panel.grid.minor.x=element_blank(),
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent", colour = NA),
    legend.box.background = element_rect(fill = "transparent", colour = NA),
    
    # Make all text white
    text = element_text(colour = "white"),
   axis.text.y = element_text(colour = "white", size=12),
    axis.text.x = element_text(colour = "white", size=9, angle = 30, hjust = 1, vjust = 1),
    
    # Make gridlines white
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    
    # Make borders and axis lines white
    panel.border = element_rect(colour = "white", fill = "transparent"),
    axis.line = element_line(colour = "white"),
    axis.ticks.x = element_line(colour = "white"),
    axis.ticks.y = element_line(colour = "white"),
    
    legend.key.size = unit(8, "pt") 
 )
    
  
    
```

{{< pagebreak >}}

#### High Speed Running Distance and HSR Distance/Min By Player (per half)



```{r md_by_player_hsr_distance,  fig.width=9.5,fig.height=2.8, dpi = 600, dev.args = list(bg = "transparent")}

md_distance_by_player %>% 
  ggplot(aes(x = str_extract(athlete_name,"(?<=\\s)[[:graph:]]+$"), y = high_speed_distance, fill = period_name, label=round(high_speed_distance)))+
  geom_col(position = position_stack(reverse = TRUE))+
      # geom_text_repel(position = position_stack(vjust = 0.5),segment.colour = NA, direction = "y", size=3,seed=42,color="white") +
  geom_text(position = position_stack(vjust = 0.5, reverse = TRUE),color="white", size=3,check_overlap=T)+
   labs(x=NULL, y ="HSR Distance (m)",fill=NULL)+
   theme_bw()+ 
  scale_y_continuous(expand = expansion(mult = c(0, 0.05)))+
    scale_fill_manual(values=c("#572C5F","#00B0B9"))+
  theme(legend.position = "bottom",legend.direction = "horizontal",panel.grid.major.x=element_blank(), panel.grid.minor.x=element_blank(),
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent", colour = NA),
    legend.box.background = element_rect(fill = "transparent", colour = NA),
    
    # Make all text white
    text = element_text(colour = "white"),
   axis.text.y = element_text(colour = "white", size=12),
    axis.text.x = element_text(colour = "white", size=9, angle = 30, hjust = 1, vjust = 1),
    
    # Make gridlines white
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    
    # Make borders and axis lines white
    panel.border = element_rect(colour = "white", fill = "transparent"),
    axis.line = element_line(colour = "white"),
    axis.ticks.x = element_line(colour = "white"),
    axis.ticks.y = element_line(colour = "white"),
    
    legend.key.size = unit(8, "pt") 
 )

```

```{r md_by_player_hsr_distance_per_min,  fig.width=9.5,fig.height=2.8, dpi = 600, dev.args = list(bg = "transparent")}


md_distance_by_player %>% 
  ggplot(aes(x = str_extract(athlete_name,"(?<=\\s)[[:graph:]]+$"), y = high_speed_distance_per_min))+
  geom_col(aes(fill = period_name),position=position_dodge2(width=0.9,preserve = "single")) +
    geom_text(aes(group =period_name,label=round(high_speed_distance_per_min,2)),size=3, vjust = -0.5, color="white", position=position_dodge2(width=0.9,preserve = "single")) +
   labs(x=NULL, y ="HSR Distance per Min (m/min)",fill=NULL)+
   theme_bw()+ 
  scale_y_continuous(expand = expansion(mult = c(0, 0.12)))+
    scale_fill_manual(values=c("#572C5F","#00B0B9"))+
  theme(legend.position = "bottom",legend.direction = "horizontal",panel.grid.major.x=element_blank(), panel.grid.minor.x=element_blank(),
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent", colour = NA),
    legend.box.background = element_rect(fill = "transparent", colour = NA),
    
    # Make all text white
    text = element_text(colour = "white"),
   axis.text.y = element_text(colour = "white", size=12),
    axis.text.x = element_text(colour = "white", size=9, angle = 30, hjust = 1, vjust = 1),
    
    # Make gridlines white
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    
    # Make borders and axis lines white
    panel.border = element_rect(colour = "white", fill = "transparent"),
    axis.line = element_line(colour = "white"),
    axis.ticks.x = element_line(colour = "white"),
    axis.ticks.y = element_line(colour = "white"),
    
    legend.key.size = unit(8, "pt") 
 )
    
  
```

{{< pagebreak >}}

#### Sprint Distance and Sprint Distance/Min By Player (per half)


```{r md_by_player_sprint_distance,  fig.width=9.5,fig.height=2.8, dpi = 600, dev.args = list(bg = "transparent")}

md_distance_by_player %>% 
  ggplot(aes(x = str_extract(athlete_name,"(?<=\\s)[[:graph:]]+$"), y = sprint_distance, fill = period_name, label=round(sprint_distance)))+
  geom_col(position = position_stack(reverse = TRUE))+
  # geom_bar_text(position = "stack", grow=T, reflow = T,contrast=T, colour="white") +
  # geom_text_repel(position = position_stack(vjust = 0.5),segment.colour = NA, direction = "y", size=3,seed=42,color="white") +
  geom_text(position = position_stack(vjust = 0.5, reverse = TRUE),color="white", size=3,check_overlap=T)+
  labs(x=NULL, y ="Sprint Distance (m)",fill=NULL)+
  theme_bw()+ 
  scale_y_continuous(expand = expansion(mult = c(0, 0.05)))+
    scale_fill_manual(values=c("#572C5F","#00B0B9"))+
      # scale_color_manual(values=c("#00B0B9","#572C5F"))+
  theme(legend.position = "bottom",legend.direction = "horizontal", panel.grid.major.x=element_blank(), panel.grid.minor.x=element_blank(),
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent", colour = NA),
    legend.box.background = element_rect(fill = "transparent", colour = NA),
    
    # Make all text white
    text = element_text(colour = "white"),
   axis.text.y = element_text(colour = "white", size=12),
    axis.text.x = element_text(colour = "white", size=9, angle = 30, hjust = 1, vjust = 1),
    
    # Make gridlines white
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    
    # Make borders and axis lines white
    panel.border = element_rect(colour = "white", fill = "transparent"),
    axis.line = element_line(colour = "white"),
    axis.ticks.x = element_line(colour = "white"),
    axis.ticks.y = element_line(colour = "white"),
    
 legend.key.size = unit(8, "pt") 
 )
```


```{r md_by_player_sprint_distance_per_min,  fig.width=9.5,fig.height=2.8, dpi = 600, dev.args = list(bg = "transparent")}

md_distance_by_player %>% 
  ggplot(aes(x = str_extract(athlete_name,"(?<=\\s)[[:graph:]]+$"), y = sprint_distance_per_min))+
  geom_col(aes(fill = period_name),position=position_dodge2(width=0.9,preserve = "single")) +
    geom_text(aes(group =period_name,label=round(sprint_distance_per_min,2)),size=3, vjust = -0.5, color="white", position=position_dodge2(width=0.9,preserve = "single")) +
   labs(x=NULL, y ="Sprint Distance per Min (m/min)",fill=NULL)+
   theme_bw()+ 
  scale_y_continuous(expand = expansion(mult = c(0, 0.12)))+
    scale_fill_manual(values=c("#572C5F","#00B0B9"))+
  theme(legend.position = "bottom",legend.direction = "horizontal",panel.grid.major.x=element_blank(), panel.grid.minor.x=element_blank(),
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent", colour = NA),
    legend.box.background = element_rect(fill = "transparent", colour = NA),
    
    # Make all text white
    text = element_text(colour = "white"),
   axis.text.y = element_text(colour = "white", size=12),
    axis.text.x = element_text(colour = "white", size=9, angle = 30, hjust = 1, vjust = 1),
    
    # Make gridlines white
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    
    # Make borders and axis lines white
    panel.border = element_rect(colour = "white", fill = "transparent"),
    axis.line = element_line(colour = "white"),
    axis.ticks.x = element_line(colour = "white"),
    axis.ticks.y = element_line(colour = "white"),
    
    legend.key.size = unit(8, "pt")
 )
    
```

{{< pagebreak >}}

```{=typst}

// Page 8 Section Divider
#section-page("{{< meta image2 >}}", "MATCH DAY COMPARISON")
```

{{< pagebreak >}}


```{r}

md_distance_team_total <- stats_period %>%
  dplyr::filter(position_name != "Goal Keeper" & tag_name == "MD" & date >= as.Date("2026-04-01") & date <= (stats_period %>% filter(activity_name == md_input) %>% pull(date) %>% unique) & str_detect(period_name, "^\\d{1,2}\\. [[:alpha:]]{5,6} Half$")) %>%
  select(activity_name, date, athlete_name, period_name, field_time, total_distance, high_speed_distance, sprint_distance) %>%
  mutate(across(where(is.numeric), ~if_else(field_time == 0 & total_distance == 0, NA_real_, .x))) %>%
  group_by(activity_name, date) %>%
  summarize(across(where(is.numeric), ~sum(.x,na.rm=T))) %>%
  ungroup %>% 
  mutate(across(where(is.numeric) & !field_time, ~.x/(field_time/60), .names="{.col}_per_min"),
         logo = case_when(str_detect(activity_name, "Montreal") ~"Montreal.png",
                       str_detect(activity_name, "Ottawa") ~ "Ottawa.png",
                       str_detect(activity_name, "Toronto") ~ "Toronto.png",
                       str_detect(activity_name, "Calgary") ~ "Calgary.png",
                       str_detect(activity_name, "Vancouver") ~ "Vancouver.png",
                       str_detect(activity_name, "Portsmouth") ~ "Portsmouth.png",
                       str_detect(activity_name, "Everton") ~ "Everton.png",
                       str_detect(activity_name, "West Ham") ~ "West Ham.png",
                       str_detect(activity_name, "AUS") ~ "AUS.png")) %>% 
  arrange(date) %>% 
  mutate(date=factor(date, levels = unique(date), labels = format(date, "%b %d")),
         Group="group"
         # ,
         # logo=paste0("<img src='", logo,  "' height='30' />")
         )

md_distance_desc <- md_distance_team_total %>% 
  mutate(across(where(is.numeric), ~mean(.x), .names="{.col}_mean"), 
         across(where(is.numeric) & !contains("_mean"), ~sd(.x), .names="{.col}_sd")) %>% 
  select(contains("mean") | contains("sd")) %>% 
  unique

```



```{r md_comparison_total_distance,  fig.width=9.5,fig.height=3, dpi = 600, dev.args = list(bg = "transparent")}


md_distance_team_total %>% 
  ggplot(aes(x = date, y = total_distance)) +
  geom_hline(yintercept=md_distance_desc$total_distance_mean, color="#00B0B9", linetype="dashed") +
  geom_hline(yintercept=md_distance_desc$total_distance_mean-2*md_distance_desc$total_distance_sd, color="red", linetype="dashed") +
  geom_hline(yintercept=md_distance_desc$total_distance_mean+2*md_distance_desc$total_distance_sd, color="red", linetype="dashed") +
  geom_line(aes(group=Group), color="white")+
  geom_image(aes(image=logo),by="width", size=0.1) + 
  geom_text(aes(label=round(total_distance)), vjust=-2, color="white") + 
  labs(x=NULL, y ="Total Distance (m)",fill=NULL)+
  theme_bw()+
  theme(panel.grid.major.x=element_blank(), panel.grid.minor.x=element_blank(),
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent", colour = NA),
    legend.box.background = element_rect(fill = "transparent", colour = NA),
    
    # Make all text white
    text = element_text(colour = "white"),
    axis.text = element_text(colour = "white"),
    
    # Make gridlines white
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    
    # Make borders and axis lines white
    panel.border = element_rect(colour = "white", fill = "transparent"),
    axis.line = element_line(colour = "white"),
    axis.ticks.x = element_line(colour = "white"),
    axis.ticks.y = element_line(colour = "white")
 )+
  scale_y_continuous(expand = expansion(mult = c(0.08, 0.2)))


    

    
```



```{r md_comparison_total_distance_per_min,  fig.width=9.5,fig.height=3, dpi = 600, dev.args = list(bg = "transparent")}


md_distance_team_total %>% 
  ggplot(aes(x = date, y = total_distance_per_min)) +
  geom_hline(yintercept=md_distance_desc$total_distance_per_min_mean, color="#00B0B9", linetype="dashed") +
  geom_hline(yintercept=md_distance_desc$total_distance_per_min_mean-2*md_distance_desc$total_distance_per_min_sd, color="red", linetype="dashed") +
  geom_hline(yintercept=md_distance_desc$total_distance_per_min_mean+2*md_distance_desc$total_distance_per_min_sd, color="red", linetype="dashed") +
  geom_line(aes(group=Group), color="white")+
  geom_image(aes(image=logo),by="width", size=0.1) + 
  geom_text(aes(label=round(total_distance_per_min)), vjust=-2, color="white") + 
  labs(x=NULL, y ="Total Distance per Min (m/min)",fill=NULL)+
  theme_bw()+
  theme(panel.grid.major.x=element_blank(), panel.grid.minor.x=element_blank(),
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent", colour = NA),
    legend.box.background = element_rect(fill = "transparent", colour = NA),
    
    # Make all text white
    text = element_text(colour = "white"),
    axis.text = element_text(colour = "white"),
    
    # Make gridlines white
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    
    # Make borders and axis lines white
    panel.border = element_rect(colour = "white", fill = "transparent"),
    axis.line = element_line(colour = "white"),
    axis.ticks.x = element_line(colour = "white"),
    axis.ticks.y = element_line(colour = "white")
 )+
  scale_y_continuous(expand = expansion(mult = c(0.08, 0.2)))


    

    
```

{{< pagebreak >}}

```{r md_comparison_hsr_distance,  fig.width=9.5,fig.height=3, dpi = 600, dev.args = list(bg = "transparent")}

md_distance_team_total %>% 
  ggplot(aes(x = date, y =high_speed_distance )) +
  geom_hline(yintercept=md_distance_desc$high_speed_distance_mean, color="#00B0B9", linetype="dashed") +
  geom_hline(yintercept=md_distance_desc$high_speed_distance_mean-2*md_distance_desc$high_speed_distance_sd, color="red", linetype="dashed") +
  geom_hline(yintercept=md_distance_desc$high_speed_distance_mean+2*md_distance_desc$high_speed_distance_sd, color="red", linetype="dashed") +
  geom_line(aes(group=Group), color="white")+
  geom_image(aes(image=logo),by="width", size=0.1) + 
  geom_text(aes(label=round(high_speed_distance)), vjust=-2, color="white") + 
  labs(x=NULL, y ="HSR Distance (m)",fill=NULL)+
  theme_bw()+
  theme(panel.grid.major.x=element_blank(), panel.grid.minor.x=element_blank(),
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent", colour = NA),
    legend.box.background = element_rect(fill = "transparent", colour = NA),
    
    # Make all text white
    text = element_text(colour = "white"),
    axis.text = element_text(colour = "white"),
    
    # Make gridlines white
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    
    # Make borders and axis lines white
    panel.border = element_rect(colour = "white", fill = "transparent"),
    axis.line = element_line(colour = "white"),
    axis.ticks.x = element_line(colour = "white"),
    axis.ticks.y = element_line(colour = "white")
 )+
  scale_y_continuous(expand = expansion(mult = c(0.08, 0.2)))


```



```{r md_comparison_hsr_distance_per_min,  fig.width=9.5,fig.height=3, dpi = 600, dev.args = list(bg = "transparent")}


md_distance_team_total %>% 
  ggplot(aes(x = date, y = high_speed_distance_per_min)) +
  geom_hline(yintercept=md_distance_desc$high_speed_distance_per_min_mean, color="#00B0B9", linetype="dashed") +
  geom_hline(yintercept=md_distance_desc$high_speed_distance_per_min_mean-2*md_distance_desc$high_speed_distance_per_min_sd, color="red", linetype="dashed") +
  geom_hline(yintercept=md_distance_desc$high_speed_distance_per_min_mean+2*md_distance_desc$high_speed_distance_per_min_sd, color="red", linetype="dashed") +
  geom_line(aes(group=Group), color="white")+
  geom_image(aes(image=logo),by="width", size=0.1) + 
  geom_text(aes(label=round(high_speed_distance_per_min,2)), vjust=-2, color="white") + 
  labs(x=NULL, y ="HSR Distance per Min (m/min)",fill=NULL)+
  theme_bw()+
  theme(panel.grid.major.x=element_blank(), panel.grid.minor.x=element_blank(),
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent", colour = NA),
    legend.box.background = element_rect(fill = "transparent", colour = NA),
    
    # Make all text white
    text = element_text(colour = "white"),
    axis.text = element_text(colour = "white"),
    
    # Make gridlines white
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    
    # Make borders and axis lines white
    panel.border = element_rect(colour = "white", fill = "transparent"),
    axis.line = element_line(colour = "white"),
    axis.ticks.x = element_line(colour = "white"),
    axis.ticks.y = element_line(colour = "white")
 )+
  scale_y_continuous(expand = expansion(mult = c(0.08, 0.2)))


    

    
```

{{< pagebreak >}}

```{r md_comparison_sprint_distance,  fig.width=9.5,fig.height=3, dpi = 600, dev.args = list(bg = "transparent")}

md_distance_team_total %>% 
  ggplot(aes(x = date, y =sprint_distance )) +
  geom_hline(yintercept=md_distance_desc$sprint_distance_mean, color="#00B0B9", linetype="dashed") +
  geom_hline(yintercept=md_distance_desc$sprint_distance_mean-2*md_distance_desc$sprint_distance_sd, color="red", linetype="dashed") +
  geom_hline(yintercept=md_distance_desc$sprint_distance_mean+2*md_distance_desc$sprint_distance_sd, color="red", linetype="dashed") +
  geom_line(aes(group=Group), color="white")+
  geom_image(aes(image=logo),by="width", size=0.1) + 
  geom_text(aes(label=round(sprint_distance)), vjust=-2, color="white") +
  labs(x=NULL, y ="Sprint Distance (m)",fill=NULL)+
  theme_bw()+
  theme(panel.grid.major.x=element_blank(), panel.grid.minor.x=element_blank(),
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent", colour = NA),
    legend.box.background = element_rect(fill = "transparent", colour = NA),
    
    # Make all text white
    text = element_text(colour = "white"),
    axis.text = element_text(colour = "white"),
    
    # Make gridlines white
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    
    # Make borders and axis lines white
    panel.border = element_rect(colour = "white", fill = "transparent"),
    axis.line = element_line(colour = "white"),
    axis.ticks.x = element_line(colour = "white"),
    axis.ticks.y = element_line(colour = "white")
 )+
  scale_y_continuous(expand = expansion(mult = c(0.08, 0.2)))


```


```{r md_comparison_sprint_distance_per_min,  fig.width=9.5,fig.height=3, dpi = 600, dev.args = list(bg = "transparent")}


md_distance_team_total %>% 
  ggplot(aes(x = date, y =sprint_distance_per_min)) +
   geom_hline(yintercept=md_distance_desc$sprint_distance_per_min_mean, color="#00B0B9", linetype="dashed") +
  geom_hline(yintercept=md_distance_desc$sprint_distance_per_min_mean-2*md_distance_desc$sprint_distance_per_min_sd, color="red", linetype="dashed") +
  geom_hline(yintercept=md_distance_desc$sprint_distance_per_min_mean+2*md_distance_desc$sprint_distance_per_min_sd, color="red", linetype="dashed") +
  geom_line(aes(group=Group), color="white")+
  geom_image(aes(image=logo),by="width", size=0.1) + 
  geom_text(aes(label=round(sprint_distance_per_min,2)), vjust=-2, color="white") + 
  labs(x=NULL, y ="Sprint Distance per Min (m/min)",fill=NULL)+
  theme_bw()+
  theme(panel.grid.major.x=element_blank(), panel.grid.minor.x=element_blank(),
    panel.background = element_rect(fill ="transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent", colour = NA),
    legend.box.background = element_rect(fill = "transparent", colour = NA),
    
    # Make all text white
    text = element_text(colour = "white"),
    axis.text = element_text(colour = "white"),
    
    # Make gridlines white
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    
    # Make borders and axis lines white
    panel.border = element_rect(colour = "white", fill = "transparent"),
    axis.line = element_line(colour = "white"),
    axis.ticks.x = element_line(colour = "white"),
    axis.ticks.y = element_line(colour = "white")
 )+
  scale_y_continuous(expand = expansion(mult = c(0.08, 0.2)))


    

    
```

{{< pagebreak >}}

```{=typst}
// Page 12 Section Divider
#section-page("{{< meta image3 >}}", "DISTANCE ACROSS THE MATCH")
```

{{< pagebreak >}}


```{r 15min_distance}

md_distance_15min_temp <- stats_period %>%
  filter(position_name != "Goal Keeper" & activity_name == md_input & str_detect(period_name, "^\\d{1,2}\\. [[:alpha:]]{5,6} Half$")) %>%
  select(activity_name, date, athlete_name, period_name,start_time, field_time, total_distance, high_speed_distance, sprint_distance) %>%
  mutate(across(where(is.numeric), ~if_else(field_time == 0 & total_distance == 0, NA_real_, .x))) %>%
  group_by(activity_name, date, period_name, start_time) %>%
  summarize(across(where(is.numeric), ~sum(.x,na.rm=T))) %>%
  ungroup %>% 
  mutate(across(where(is.numeric) & !field_time, ~.x/(field_time/60), .names="{.col}_per_min")) %>% 
  arrange(start_time) %>% 
  mutate(
    # period_name = paste(str_remove(period_name, "\\d{1,2}\\.\\s"), (row_number()-1)*(90/n()), "-", row_number()*(90/n()), "min"),
    period=paste0((row_number()-1)*(90/n()), "-", row_number()*(90/n()), "min"),
    position_name="All", 
    across(contains("distance")& !contains("per_min"), ~.x/10))


 md_distance_15min_by_position <- stats_period %>%
      dplyr::filter(position_name != "Goal Keeper" & activity_name == md_input &  str_detect(period_name, "^\\d{1,2}\\. [[:alpha:]]{5,6} Half$")) %>%
      select(activity_name, date, athlete_name, position_name, period_name,start_time, field_time, total_distance, high_speed_distance, sprint_distance) %>%
      mutate(across(where(is.numeric), ~if_else(field_time == 0 & total_distance == 0, NA_real_, .x)),
             position_name = case_when(str_detect(position_name, "Back") | str_detect(position_name, "Defender")~ "Defender",
                              str_detect(position_name, "Midfielder")~ "Midfielder",
                              str_detect(position_name, "Winger") | str_detect(position_name, "Striker")~ "Attacker",
                              .default=position_name)) %>%
      group_by(activity_name, date, period_name, start_time, position_name) %>%
      summarize(across(where(is.numeric), ~sum(.x,na.rm=T))) %>%
      ungroup %>% 
      mutate(across(where(is.numeric) & !field_time, ~.x/(field_time/60), .names="{.col}_per_min")) %>% 
      arrange(start_time) %>% 
      group_by(position_name) %>% 
      mutate(
        # period_name = paste(str_remove(period_name, "\\d{1,2}\\.\\s"), (row_number()-1)*(90/n()), "-", row_number()*(90/n()), "min"),
        period=paste0((row_number()-1)*(90/n()), "-", row_number()*(90/n()), "min"),
    across(contains("distance") & !contains("per_min"), ~if_else(position_name == "Defender",.x/4,.x/3))) %>% 
      ungroup 
 
md_distance_15min <- rbind(md_distance_15min_temp, md_distance_15min_by_position) 

 
```

```{r 15min_total_distance,  fig.width=9.5,fig.height=6, dpi = 600, dev.args = list(bg = "transparent")}

md_distance_15min %>% 
ggplot(aes(x=factor(period), y=total_distance, color=position_name)) +
  geom_point()+
  geom_line(aes(group=position_name))+
  labs(x=NULL, y="Total Distance (m)", color=NULL)+
  theme_bw()+
  theme(legend.position = "bottom", legend.direction="horizontal",
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent", colour = NA),
    legend.box.background = element_rect(fill = "transparent", colour = NA),
    
    # Make all text white
    text = element_text(colour = "white"),
    axis.text = element_text(colour = "white"),
    
    # Make gridlines white
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    
    # Make borders and axis lines white
    panel.border = element_rect(colour = "white", fill = "transparent"),
    axis.line = element_line(colour = "white"),
    axis.ticks.x = element_line(colour = "white"),
    axis.ticks.y = element_line(colour = "white")
 ) +
  scale_color_manual(values=c("red", "#00B0B9","#572C5F","#B2C9D4"))

   
```

{{< pagebreak >}}

```{r 15min_hsr_distance,  fig.width=9.5,fig.height=6, dpi = 600, dev.args = list(bg = "transparent")}

md_distance_15min %>% 
ggplot(aes(x=factor(period), y=high_speed_distance, color=position_name)) +
  geom_point()+
  geom_line(aes(group=position_name))+
  labs(x=NULL, y="HSR Distance (m)", color=NULL)+
  theme_bw()+
  theme(legend.position = "bottom", legend.direction="horizontal",
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent", colour = NA),
    legend.box.background = element_rect(fill = "transparent", colour = NA),
    
    # Make all text white
    text = element_text(colour = "white"),
    axis.text = element_text(colour = "white"),
    
    # Make gridlines white
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    
    # Make borders and axis lines white
    panel.border = element_rect(colour = "white", fill = "transparent"),
    axis.line = element_line(colour = "white"),
    axis.ticks.x = element_line(colour = "white"),
    axis.ticks.y = element_line(colour = "white")
 )+
  scale_color_manual(values=c("red", "#00B0B9","#572C5F","#B2C9D4"))

   
```

{{< pagebreak >}}

```{r 15min_sprint_distance, fig.width=9.5,fig.height=6, dpi = 600, dev.args = list(bg = "transparent")}

md_distance_15min %>% 
ggplot(aes(x=factor(period), y=sprint_distance, color=position_name)) +
  geom_point()+
  geom_line(aes(group=position_name))+
  labs(x=NULL, y="Sprint Distance (m)", color=NULL)+
  theme_bw()+
  theme(legend.position = "bottom", legend.direction="horizontal",
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent", colour = NA),
    legend.box.background = element_rect(fill = "transparent", colour = NA),
    
    # Make all text white
    text = element_text(colour = "white"),
    axis.text = element_text(colour = "white"),
    
    # Make gridlines white
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    
    # Make borders and axis lines white
    panel.border = element_rect(colour = "white", fill = "transparent"),
    axis.line = element_line(colour = "white"),
    axis.ticks.x = element_line(colour = "white"),
    axis.ticks.y = element_line(colour = "white")
 )+
  scale_color_manual(values=c("red", "#00B0B9","#572C5F","#B2C9D4"))

   
```